\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyperref}
\input{glyphtounicode}

% \documentclass[letterpaper,11pt]{article}

% \usepackage{newtxtext}
% \usepackage{newtxmath}

% \usepackage[empty]{fullpage}
% \usepackage{titlesec}
% \usepackage{marvosym}
% \usepackage[usenames,dvipsnames]{color}
% \usepackage{verbatim}
% \usepackage{enumitem}
% \usepackage[hidelinks]{hyperref}
% \usepackage{fancyhdr}
% \usepackage[english]{babel}
% \usepackage{tabularx}
% \usepackage{hyperref}
% \input{glyphtounicode}

% ----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Ahmad } \\ \vspace{1pt}
  \small +92-3020511167 $|$
  \href{mailto:ahmadjajja86@gmail.com}{\underline{ahmadjajja86@gmail.com}} $|$
  \href{https://www.linkedin.com/in/ahmad-jajja/}{\underline{linkedin.com/in/ahmad-jajja}} $|$
  \href{https://github.com/Ahmadjajja}{\underline{gitub.com/Ahmadjajja}} $|$
  \href{https://linktr.ee/Ahmadjajja}{\underline{linktr.ee/Ahmadjajja}}
  % \href{https://leetcode.com/ahmadjajja86/}{\underline{leetcode}} $|$
  % \href{https://ahmad-jajja.netlify.app/}{\underline{website}}
  % \textbf{\Huge \scshape Ahmad Jajja} \\ \vspace{1pt}
  % \footnotesize +92-3020511167 $|$ 
  % \href{mailto:ahmadjajja86@gmail.com}{\underline{ahmadjajja86@gmail.com}} $|$ 
  % \href{https://www.linkedin.com/in/ahmad-jajja-ba8b34210/}{\underline{linkedin.com/in/ahmad-jajja}} $|$
  % \href{https://github.com/Ahmadjajja}{\underline{github.com/Ahmadjajja}} $|$
  % \href{https://leetcode.com/ahmadjajja86/}{\underline{leetcode.com/ahmadjajja86}}
\end{center}

%-----------1 - EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{The University of Agriculture \hspace{3.5cm} CGPA: 3.00 / 4.00}{Faisalabad,PK}
% {CGPA: 3.90 / 4.00}{}
{Bachelor of Science in Computer Science}{Sep. 2020 -- June 2024}
\resumeItemListStart
\resumeItem{Relevant Coursework: Design and Analysis of Algorithms, Data Structures and Algorithms, Programming Fundamentals, Object-Oriented Programming, Web Development, Artificial Intelligence, Databases, Visual Programming, Mathematics (Linear Algebra, Derivatives, and Integration), Statistics, Cloud Computing, Internet of Things.}
\resumeItemListEnd
\resumeSubHeadingListEnd
%

%-----------2 - Hackathons & Competitions-----------
\section{Hackathons and Competitions}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/Louvivien/AIpodcastgenerator}{\underline{AI Podcast Generator}}} $|$ \emph{HTML, CSS, Bootstrap5, Javascript, React, Generative AI, Langchain, python}}{}
\resumeItemListStart
\resumeItem{Worked with a team of six individuals from the USA, Chile, France, and Pakistan in an international hackathon, collaborating on the AI Podcaster Generator Project.}
\resumeItem{This project transforms written content into captivating, lifelike podcasts effortlessly using ElevenLabs API-powered speech synthesis.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\href{https://shorturl.at/kHNZ2}{\underline{Meta Hackar Cup'23 Qualifier}}}}{}
\resumeItemListStart
\resumeItem{I participated in the Meta Hacker Cup during the practice round, successfully solving 4 out of 5 problems, and qualified for the first round. I secured the 22nd position in Pakistan.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\href{https://shorturl.at/myRTX}{\underline{Google Code Jam'23 Qualifier}}}}{}
\resumeItemListStart
\resumeItem{I participated in the Google Code Jam coding competition organized by Google and learned a lot from this coding competition, successfully solving 2 out of 4 questions.}
\resumeItemListEnd
\resumeSubHeadingListEnd
%


%-----------3 - PERSONAL PROJECTS-----------
\section{Personal Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/Ahmadjajja/React_Bank}{\underline{Full Stack Bank WEB APP}}} $|$ \emph{HTML, CSS, Bootstrap5, Javascript, React, Context API, Firebase, Firestore}}{}
\resumeItemListStart
\resumeItem{Bank-App is a web application allowing users to manage accounts, perform
  transactions, and view transaction history conveniently.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\href{https://github.com/Ahmadjajja/Social_Real_Estate_System_Mobile_App_Frontend}{\underline{Full Stack Real Estate Mobile App}}} $|$ \emph{Javascript, ReactNative, Redux, ContextAPI, NodeJS,
    ExpressJS, MongoDB}}{}
\resumeItemListStart
\resumeItem{Real-Estate Mobile App with authentication, dashboard, property
  management, searching, browsing and call-to-action feature for property
  tansactions, powered by REST APIs using Node JS.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\href{https://github.com/Ahmadjajja/E_Commerce_Mobile_App_Frontend}{\underline{Full Stack E-Commerce Mobile App}}} $|$ \emph{Javascript, ReactNative, Redux, ContextAPI, NodeJS,
    ExpressJS, MongoDB}}{}
\resumeItemListStart
\resumeItem{E-commerce mobile app with user registration, product catalog, cart, wishlist,
  checkout, payment, order tracking, and admin dashboard.}
\resumeItemListEnd
\resumeSubHeadingListEnd
%

%-----------4 - EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{MERN Stack Trainer}{Dec 2022 -- Present}
{Saylani Mass IT Training Program}{Faisalabad, PK}
\resumeItemListStart
\resumeItem{My role involves delivering {\href{https://www.linkedin.com/posts/ahmad-jajja-ba8b34210_webdevelopment-learningtogether-activity-7094647856233365504-rAtx?utm_source=share&utm_medium=member_desktop}{\underline{sessions}}} on HTML5, CSS3, Bootstrap5, Javascript, Typescript, ReactJS, ReactNative, Redux, ContextAPI, NodeJS,
  ExpressJS, MongoDb, Firebase, Firestore, Git, Github, Heroku, Netlify, Surge}
% \resumeItem{Instructed nearly 200 students.}
% \resumeItem{My role involves delivering comprehensive training sessions on theMERN stack}
% \resumeItem{Providing instructions in various hosting and version control platforms}
\resumeItemListEnd
\resumeSubheading
{MERN Stack Developer}{Sep 2022 - Mar 2023}
{ZW Tech}{Faisalabad, PK}
\resumeItemListStart
\resumeItem{Modified React JS front-end for UAE recruitment business website, resembling LinkedIn.}
\resumeItem{Developed Node.js-based GraphQL APIs, enhancing data management and integration
  for Dashboard.}
\resumeItem{Led the Desgning team and collaborated with product managers, business partners, and
  engineers to help define product requirements and roadmap .}
\resumeItemListEnd

\resumeSubheading
{MERN Stack Developer}{May 2022 - Aug 2022}
{Seeraht}{Faisalabad, PK}
\resumeItemListStart
\resumeItem{Developed and maintained MERN web apps at Seeraht, prioritizing quality, scalability, and
  efficiency.}
\resumeItem{Collaborated with cross-functional teams, implementing complex software features
  using modern development techniques.}
\resumeItem{Experience in integrating web applications with third-party APIs and services.}
%         \resumeItem{Performed code reviews, troubleshooted code issues, and actively participated in the

%
% software development lifecycle. Utilized MERN stack, Agile practices, and effective
% communication for transformative web applications.}
\resumeItemListEnd
% \resumeSubheading
% {MERN Stack Developer}{Nov 2021 - Present}
% {Fb and local Clients}{Faisalabad, PK}
% \resumeItemListStart
%   \resumeItem{
%     Developed and delivered a wide range of web-based solutions, utilizing front-end technologies such as HTML, CSS, and JavaScript, as well as back-end technologies such as Node.js and Express js.}
%   \resumeItem{
%     Built and maintained strong relationships with clients through effective communication and problem-solving skills, ensuring timely completion and adherence to project requirements.}
%   \resumeItem{Accomplished in utilizing version control systems such as Git and SVN, and implementing agile methodologies for efficient project management.}
%   \resumeItem{Proven ability to work independently as well as part of a team, successfully delivering projects on time and within budget.}
%   \resumeItem{
%     Experience in integrating web applications with third-party APIs and services.}
% \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------5 - PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: JavaScript (ES6+), Typescript, Java, C, C++, Dart, Python } \\
        \textbf{Frontend}{: HTML5, CSS3, SCSS, Chakra-UI, Ant-Design, Bootstrap-5, React-JS, React-Native, ContextAPI, Redux} \\
        \textbf{Backend}{: Node-JS, Express-JS, Firebase} \\
        \textbf{Version Control}{: Git, Github} \\
        \textbf{APIs}{: Rest-APIs, GraphQL} \\
        \textbf{Databases}{: MongoDB, Firestore}\\
        }}
\end{itemize}
%

%-----------6 - ACHIEVEMENTS-----------
\section{Achievements}
% \resumeSubHeadingListStart
\resumeItemListStart
\resumeItem{Solved over 200 Data Structures and Algorithms problems on {\href{https://leetcode.com/ahmadjajja86/}{\underline{leetcode}}}.}
\resumeItem{I {\href{https://www.linkedin.com/posts/ahmad-jajja-ba8b34210_webdevelopment-learningtogether-activity-7094647856233365504-rAtx?utm_source=share&utm_medium=member_desktop}{\underline{trained}}} over 300 students at the Saylani Mass IT Training Program in Web Development.}
% \resumeItem{Completed one year Web and Mobile App Development Bootcamp from
%     {\href{https://drive.google.com/file/d/1HAMbxoTU0kpSDj8k-YFjYE14ngWeisZ1/view}{\underline{Saylani Mass IT Training Programs(SMIT).}}}}
\resumeItemListEnd
% \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
